# Continuous Distributions


**Chapter Preview**

This table of distributions is a summary of selected continuous probability distributions used throughout *Loss Data Analytics*.

```{r eval=TRUE, include=FALSE}
require(actuar)
```

## One Parameter Distributions

<div class="tab">
  <button class="tablinks" onclick="openTab(event, '1pA')">Exponential</button>
  <button class="tablinks" onclick="openTab(event, '1pB')">Inv Exponential</button>
</div>


<div id="1pA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Exponential</h3>
  <p>

**Exponential Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & \theta>0 \\
\hline
  \small{\text{Probability density}} & \frac{1}{\theta}e^{-x/\theta} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-e^{-x/\theta} \\
   ~~F(x) & \\
\hline
 \textit{k}^{th}~\small{\text{raw moment}}  & \theta^k\Gamma(k+1) \\
  ~~\mathrm{E}[X^k]  & k>-1 \\
\hline
  VaR_p(x) & -\theta \ln (1-p) \\
\hline
  \small{\text{Limited Expected Value}} & \theta(1-e^{-x/\theta}) \\
  ~~\mathrm{E}[X\wedge x] & \\
\hline
\end{array}
\end{matrix}
$$
```{r}
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dexp(X,rate=1/theta),type="l",
     ylab="Probability density",col="red",main="Exponential Distribution")
```

**Exponential `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dexp}(x=, rate=1/\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pexp}(p=, rate=1/\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qexp}(q=, rate=1/\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rexp}(n=, rate=1/\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="1pB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Inv Exponential</h3>
  <p>

**Inverse Exponential Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Probability density}} & \frac{\theta e^{-\theta/x}}{x^2} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & e^{-\theta/x} \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \theta^k\Gamma(k+1) \\
  ~~\mathrm{E}[X^k]  & k>-1 \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \theta^k\Gamma(k+1)\Gamma(k+1;x/\theta)+x^k e^{-x/\theta} \\
  & k>-1 \\
\hline
\end{array}
\end{matrix}
$$
```{r}
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dinvexp(X,scale=theta),type="l",
     ylab="Probability density",col="red",main="Inv Exponential Distribution")
```

**Inverse Exponential `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dinvexp}(x=, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pinvexp}(p=, scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qinvexp}(q=, scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rinvexp}(n=, scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

## Two Parameter Distributions


<div class="tab">
  <button class="tablinks" onclick="openTab(event, '2pA')">Pareto</button>
  <button class="tablinks" onclick="openTab(event, '2pB')">Inv Pareto</button>
  <button class="tablinks" onclick="openTab(event, '2pC')">Loglogistic</button>
  <button class="tablinks" onclick="openTab(event, '2pD')">Paralogistic</button>
  <button class="tablinks" onclick="openTab(event, '2pE')">Gamma</button>
  <button class="tablinks" onclick="openTab(event, '2pF')">Inv Gamma</button>
  <button class="tablinks" onclick="openTab(event, '2pG')">Weibull</button>
  <button class="tablinks" onclick="openTab(event, '2pH')">Inv Weibull</button>
  <button class="tablinks" onclick="openTab(event, '2pI')">Uniform</button>
  <button class="tablinks" onclick="openTab(event, '2pJ')">Normal</button>
</div>

<div id="2pA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Pareto</h3>
  <p>

**Pareto Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & \alpha>0 \\
\hline
  \small{\text{Probability density}} & \frac{\alpha\theta^\alpha}{(x+\theta)^{\alpha+1}} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-\Big(\frac{\theta}{x+\theta}\Big)^\alpha \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(k+1)\Gamma(\alpha-k)}{\Gamma(\alpha)} \\
  ~~\mathrm{E}[X^k] & -1<\alpha<k \\
\hline
  \small{\text{Limited Expected Value:}}~\alpha\neq1 & \frac{\theta}{\alpha-1}\Big[1-\Big(\frac{\theta}{x+\theta}\Big)^{\alpha-1}\Big] \\
  ~~\mathrm{E}[X\wedge x] & \\
\hline
  \small{\text{Limited Expected Value:}}~\alpha=1 & -\theta \ln \left(\frac{\theta}{x+\theta}\right) \\
  ~~\mathrm{E}[X\wedge x] & \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta^k\Gamma(k+1)\Gamma(\alpha-k)}{\Gamma(\alpha)}\beta(k+1,\alpha-k;\frac{x}{x+\theta})+x^k(\frac{\theta}{x+\theta})^\alpha  \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 3
theta = 200
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dpareto2(X,shape=alpha,scale=theta),type="l",
     ylab="Probability density",col="red",main="Pareto Distribution")
```

**Pareto `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dpareto2}(x=, shape=\alpha, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{ppareto2}(p=, shape=\alpha,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qpareto2}(q=, shape=\alpha,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rpareto2}(n=, shape=\alpha,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Inv Pareto</h3>
  <p>

**Inverse Pareto Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Probability density}} & \frac{\tau\theta x^{\tau-1}}{(x+\theta)^\tau-1} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \Big(\frac{x}{x+\theta}\Big)^\tau \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(\tau+k)\Gamma(1-k)}{\Gamma(\tau)} \\
  ~~\mathrm{E}[X^k]  & -\tau<k<1 \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \theta^k\tau\int^{x/(x+\theta)}_0~y^{\tau+k-1}(1-y)^{-k}dy+x^k[1-\Big(\frac{x}{x+\theta}\Big)^\tau] \\
  & k>-\tau \\
\hline
\end{array}
\end{matrix}
$$
```{r}
tau = 5
theta = 100
X=seq(from=0,to=3000,by=1)
plot(x=X,y=dinvpareto(X,shape=tau,scale=theta),type="l",
     ylab="Probability density",col="red",main="Inv Pareto Distribution")
```

**Inverse Pareto `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dinvpareto}(x=, shape=\tau, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pinvpareto}(p=, shape=\tau,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qinvpareto}(q=, shape=\tau,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rinvpareto}(n=, shape=\tau,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Loglogistic</h3>
  <p>

**Loglogistic Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & u=\frac{(x/\theta)^\gamma}{1+(x/\theta)^\gamma} \\
\hline
  \small{\text{Probability density}} & \frac{\gamma(x/\theta)^\gamma}{x[1+(x/\theta)^\gamma]^2} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & u \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \theta^k\Gamma(1+(k/\gamma))\Gamma(1-(k/\gamma)) \\
  ~~\mathrm{E}[X^k]  & -\gamma<k<\gamma \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \theta^k\Gamma(1+(k/\gamma))\Gamma(1-(k/\gamma))\beta(1+(k/\gamma),1-(k/\gamma);u)+x^k(1-u) \\
  & k>-\gamma \\
\hline
\end{array}
\end{matrix}
$$

```{r}
#need to write a f(x) for this dist
```

</p>
</div>

<div id="2pD" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Paralogistic</h3>
  <p>

**Paralogistic Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & u=\frac{1}{1+(x/\theta)^\alpha} \\
\hline
  \small{\text{Probability density}} & \frac{\alpha^2(x/\theta)^\alpha}{x[1+(x/\theta)^\alpha]^{\alpha+1}} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-u^\alpha \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(1+(k/\alpha))\Gamma(\alpha-(k/\alpha))}{\Gamma(\alpha)} \\
  ~~\mathrm{E}[X^k]  & -\alpha<k<\alpha^2 \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta^k\Gamma(1+(k/\alpha))\Gamma(\alpha-(k/\alpha))}{\Gamma(\alpha)}\beta(1+(k/\alpha),\alpha-(k/\alpha);1-u)+x^\alpha \\
  & k>-\alpha \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 2
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dparalogis(X,shape=alpha,scale=theta),type="l",
     ylab="Probability density",col="red",main="Paralogistic Distribution")
```

**Paralogistic `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dparalogis}(x=, shape=\alpha, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pparalogis}(p=, shape=\alpha,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qparalogis}(q=, shape=\alpha,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rparalogis}(n=, shape=\alpha,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pE" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Gamma</h3>
  <p>

**Gamma Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & \theta>0,~\alpha>0 \\
\hline
  \small{\text{Probability density}} & \frac{1}{\theta^{\alpha}\Gamma(\alpha)}x^{\alpha-1}e^{-x/\theta} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \Gamma(\alpha;\frac{x}{\theta}) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}}  & \theta^k\frac{\Gamma(\alpha+k)}{\Gamma(\alpha)} \\
  ~~\mathrm{E}[X^k]  & k>-\alpha \\
\hline
  \small{\text{Limited Expected Value}} & \frac{\theta^k\Gamma(k+\alpha)}{\Gamma(\alpha)}\Gamma(k+\alpha; x/\theta)+x^k[1-\Gamma(\alpha; x/\theta)]  \\
   ~~\mathrm{E}[X\wedge x] & k > -\alpha \\
\hline
\end{array}
\end{matrix}
$$
```{r}
alpha = 2
theta = 50
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dgamma(X,shape=alpha,scale=theta),type="l",
     ylab="Probability density",col="red",main="Gamma Distribution")
```

**Gamma `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dgamma}(x=, shape=\alpha, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pgamma}(p=, shape=\alpha,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qgamma}(q=, shape=\alpha,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rgamma}(n=, shape=\alpha,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pF" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Inv Gamma</h3>
  <p>

**Inverse Gamma Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Probability density}} & \frac{(\theta/x)^\alpha e^{-\theta/x}}{x\Gamma(\alpha)} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-\Gamma(\alpha;\theta/x) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(\alpha-k)}{\Gamma(\alpha)} \\
  ~~\mathrm{E}[X^k]  & k<\alpha \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta^k\Gamma(\alpha-k)}{\Gamma(\alpha)}[1-\Gamma(\alpha-k;\theta/x)]+x^k\Gamma(\alpha;\theta/x) \\
  &  \\
\hline
\end{array}
\end{matrix}
$$
```{r}
alpha = 3
theta = 100
X=seq(from=0,to=400,by=1)
plot(x=X,y=dinvgamma(X,shape=alpha,scale=theta),type="l",
     ylab="Probability density",col="red",main="Inv Gamma Distribution")
```

**Gamma `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dinvgamma}(x=, shape=\alpha, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pinvgamma}(p=, shape=\alpha,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qinvgamma}(q=, shape=\alpha,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rinvgamma}(n=, shape=\alpha,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pG" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Weibull</h3>
  <p>

**Weibull Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & x>0,\alpha>0 \\
\hline\
  \small{\text{Probability density}} & \frac{\alpha \Big(\frac{x}{\theta}\Big)^\alpha e^-\Big(\frac{x}{\theta}\Big)^\alpha}{x} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-\exp\Big(-\Big(\frac{x}{\theta}\Big)^\alpha\Big) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \theta^k \Gamma(1 + \frac{k}{\alpha}) \\
  ~~\mathrm{E}[X^k]  & k>-\alpha \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \theta^k\Gamma(1+\frac{k}{\alpha})\Gamma\Big[1+\frac{k}{\alpha};\Big(\frac{x}{\theta}\Big)^\alpha\Big]+x^k\exp\Big(-\Big(\frac{x}{\alpha}\Big)^\alpha\Big)  \\
   & k>-\alpha \\
\hline
\end{array}
\end{matrix}
$$
```{r}
alpha = 2
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dweibull(X,shape=alpha, scale=theta),type="l",
     ylab="Probability density",col="red",main="Weibull Distribution")
```

**Weibull `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dweibull}(x=, shape=\alpha, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pweibull}(p=, shape=\alpha,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qweibull}(q=, shape=\alpha,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rweibull}(n=, shape=\alpha,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pH" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Inv Weibull</h3>
  <p>

**Inverse Weibull Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & x>0,\alpha>0 \\
\hline\
  \small{\text{Probability density}} & \frac{\alpha(\theta/x)^\alpha \exp^{-(\theta/x)^\alpha}}{x} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \exp\Big(-\Big(\frac{\theta}{x}\Big)^\alpha\Big) \\
   ~~F(x) & \\
\hline
 \textit{k}^{th}~\small{\text{raw moment}} & \theta^k\Gamma(1-(k/\alpha)) \\
  ~~\mathrm{E}[X^k]  & k<\alpha \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \theta^k\Gamma(1-(k/\alpha))[1-\Gamma(1(k/\alpha);(\theta/x)^\alpha)]+x^k[1-e^{-(\theta/x)^\alpha}] \\
  &  \\
\hline
\end{array}
\end{matrix}
$$
```{r}
alpha = 5
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dinvweibull(X,shape=alpha,scale=theta),type="l",
     ylab="Probability density",col="red",main="Inv Weibull Distribution")
```

**Inverse Weibull `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dinvweibull}(x=, shape=\alpha, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pinvweibull}(p=, shape=\alpha,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qinvweibull}(q=, shape=\alpha,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rinvweibull}(n=, shape=\alpha,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pI" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Uniform</h3>
  <p>

**Uniform Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & -\infty<\alpha<\beta<\infty \\
\hline
  \small{\text{Probability density}} & \frac{1}{\beta-\alpha} \\
  \text{f(x)} & \\
\hline
  \small{\text{Distribution function}} & \frac{x-\alpha}{\beta-\alpha} \\
 ~~F(x) & \\
\hline
  \text{Mean} & \frac{\beta+\alpha}{2} \\
  \text{E[X]} & \\
\hline
  \text{Variance} & \frac{(\beta-\alpha)^2}{12} \\
  E[(X-\mu)^2] & \\
\hline
  \mathrm{E}[(X-\mu)^k] & \mu_k=0~~~\text{for odd }\textit{k} \\
   & \mu_k=\frac{(\beta-\alpha)^k}{2^k (k+1)}~~~\text{for even }\textit{k} \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 50
beta = 100
X=seq(alpha,beta,1)
plot(x=X,y=dunif(X,alpha,beta),type="l",
     ylab="Probability density",col="red",main="Continous Uniform Distribution")
```

**Uniform `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dunif}(x=, min=a, max=b) \\
\hline
  \small{\text{Distribution function}} & \text{punif}(p=, min=a, max=b) \\
\hline
  \small{\text{Quantile function}} & \text{qunif}(q=, min=a, max=b) \\ 
\hline
  \small{\text{Random sampling function}} & \text{runif}(n=, min=a, max=b) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>


<div id="2pJ" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Normal</h3>
  <p>

**Normal Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & -\infty<\mu<\infty,~\sigma>0 \\
\hline
  \small{\text{Probability density}} & \frac{1}{\sqrt{2\pi}\sigma} \exp\left( -\frac{(x-\mu)^2}{2\sigma^2}\right) \\
  \text{f(x)} & \\
\hline
  \small{\text{Distribution function}} & \Phi\left(\frac{x-\mu}{\sigma}\right) \\
 ~~F(x) & \\
\hline
  \text{Mean} & \mu \\
  \text{E[X]} & \\
\hline
  \text{Variance} & \sigma^2 \\
  E[(X-\mu)^2] & \\
\hline
  \mathrm{E}[(x-\mu)^k] & \mu_k=0~~~\text{for even k} \\
   & \mu_k=\frac{k!\sigma^2}{(\frac{k}{2})! 2^{k/2}}~~~\text{for odd k} \\
\hline
\end{array}
\end{matrix}
$$

```{r}
mu=100
sigma=10
X=seq(from=0,to=200,by=1)
plot(x=X,y=dnorm(X,mean=mu,sd=sigma),type="l",
     ylab="Probability density",col="red",main="Normal Distribution")
```

**Normal `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dnorm}(x=, mean=\mu, sd=\sigma) \\
\hline
  \small{\text{Distribution function}} & \text{pnorm}(p=, mean=\mu, sd=\sigma) \\
\hline
  \small{\text{Quantile function}} & \text{qnorm}(q=, mean=\mu, sd=\sigma) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rnorm}(n=, mean=\mu, sd=\sigma) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="2pK" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Cauchy</h3>
  <p>

**Cauchy Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & -\infty <\alpha <\infty, \beta>0 \\
\hline
  \small{\text{Probability density}} & \frac{1}{\pi\beta}[1+\left( \frac{x-\alpha}{\beta}\right)^2]^{-1} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 50
beta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dcauchy(X,location=alpha,scale=beta),
     type="l",ylab="Probability density",col="red",main="Cauchy Distribution")
```

**Cauchy `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dcauchy}(x=, location=\alpha, scale=\beta) \\
\hline
  \small{\text{Distribution function}} & \text{pcauchy}(p=, location=\alpha, scale=\beta) \\
\hline
  \small{\text{Quantile function}} & \text{qcauchy}(q=, location=\alpha, scale=\beta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rcauchy}(n=, location=\alpha, scale=\beta) \\
\hline
\end{array}
\end{matrix}
$$
</p>
</div>


## Three Parameter Distributions


<div class="tab">
  <button class="tablinks" onclick="openTab(event, '3pA')">Generalized Pareto</button>
  <button class="tablinks" onclick="openTab(event, '3pB')">Burr</button>
  <button class="tablinks" onclick="openTab(event, '3pC')">Inv Burr</button>
</div>

<div id="3pA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Generalized Pareto</h3>
  <p>

**Generalized Pareto Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & u=\Big(\frac{x}{x+\theta}\Big) \\
\hline
  \small{\text{Probability density}} & \frac{\Gamma(\alpha+\tau)}{\Gamma(\alpha)\Gamma(\tau)}\frac{\theta^\alpha x^{\tau-1}}{(x+\theta)^{\alpha+\tau}} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \beta(\tau,\alpha;u) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(\tau+1)\Gamma(\alpha-k)}{\Gamma(\alpha)\Gamma(\tau)} \\
  ~~~~\mathrm{E}[X^k]  & -\tau<k<\alpha \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta^k\Gamma(\tau+k)\Gamma(\alpha-k)}{\Gamma(\alpha)\Gamma(\tau)}\beta(\tau+k,\alpha-k;u)+x^k[1-\beta(\tau,\alpha,u)]  \\
  & k>-\tau \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 3
tau = 5
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dgenpareto(X,shape1=alpha,shape2=tau,scale=theta),type="l",
     ylab="Probability density",col="red",main="Generalized Pareto Distribution")
```

**Generalized Pareto `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dgenpareto}(x=, shape1=\alpha, shape2=\tau, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pgenpareto}(q=, shape1=\alpha, shape2=\tau, scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qgenpareto}(p=, shape1=\alpha, shape2=\tau, scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rgenpareto}(r=, shape1=\alpha, shape2=\tau, scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$
</p>
</div>

<div id="3pB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Burr</h3>
  <p>

**Burr Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & u=\frac{1}{1+(x/\theta)^\gamma} \\
\hline
  \small{\text{Probability density}} & \frac{\alpha\gamma(x/\theta)^\gamma}{x[1+(x/\theta)^\gamma]^{\alpha+1}} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-u^\alpha \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta\Gamma(1+(k/\gamma))\Gamma(\alpha-(k/\gamma))}{\Gamma(\alpha)} \\
  ~~~~\mathrm{E}[X^k]  & -\gamma<k<\alpha\gamma \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta\Gamma(1+(k/\gamma))\Gamma(\alpha-(k/\gamma))}{\Gamma(\alpha)}\beta(1+(k/\gamma),\alpha-(k/\gamma);1-u)+x^ku^\alpha  \\
  & k>-\tau \\
\hline
\end{array}
\end{matrix}
$$
```{r}
alpha = 2
gamma=3
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dburr(X,shape1=alpha,shape2=gamma,scale=theta),type="l",
     ylab="Probability density",col="red",main="Burr Distribution")
```

**Burr `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dburr}(x=, shape1=\alpha, shape2=\gamma, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pburr}(p=, shape1=\alpha, shape2=\gamma, scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qburr}(q=, shape1=\alpha, shape2=\gamma, scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rburr}(n=, shape1=\alpha, shape2=\gamma, scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$
</p>
</div>

<div id="3pC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Inv Burr</h3>
  <p>

**Inverse Burr Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & u=\frac{(x/\theta)^\gamma}{1+(x/\theta)^\gamma} \\
\hline
  \small{\text{Probability density}} & \frac{\alpha\gamma(x/\theta)^\gamma}{x[1+(x/\theta)^\tau]^{\alpha+1}} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & u^\tau \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(1+(k/\gamma))\Gamma(\alpha-(k/\gamma))}{\tau} \\
  ~~~~\mathrm{E}[X^k]  & -\tau\gamma<k<\gamma \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta^k\Gamma(1+(k/\gamma))\Gamma(\alpha-(k/\gamma))}{\tau}\beta(\tau+(k/\gamma),1-(k/\gamma);u)+x^k[1-u^\tau]  \\
  & k>-\tau \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 2
tau=3
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dinvburr(X,shape1=alpha,shape2=tau,scale=theta),type="l",
     ylab="Probability density",col="red",main="Inv Burr Distribution")
```

**Inverse Burr `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dinvburr}(x=, shape1=\alpha, shape2=\tau, scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pinvburr}(p=, shape1=\alpha, shape2=\tau, scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qinvburr}(q=, shape1=\alpha, shape2=\tau, scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rinvburr}(n=, shape1=\alpha, shape2=\tau, scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>



## Four Parameter Distributions


<div class="tab">
  <button class="tablinks" onclick="openTab(event, '4pA')">GB2</button>
</div>

<div id="4pA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>

<h3>GB2</h3>
  <p>

**GB2 Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & \beta>0 \\
\hline
  \small{\text{Probability density}} & \frac{a*x^{a*\alpha-1}}{b^{a*\alpha} B(\alpha,\beta)\Big[1+(x/b)^a\Big]^{\alpha+\beta}} \\
    ~~ \small{\text{function }} f(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{b^k\Big(\alpha+\frac{k}{a},\beta-\frac{k}{a}\Big)}{(\alpha,\beta)} \\
  ~~~~\mathrm{E}[X^k]  & \textit{k}>0 \\
\hline
\end{array}
\end{matrix}
$$

```{r}
#Need Density function and respective packages for graph
```

**GB2 `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{insert text}(x=,) \\
\hline
  \small{\text{Distribution function}} & \text{insert text}(q=,) \\
\hline
  \small{\text{Quantile function}} & \text{insert text}(p=,) \\ 
\hline
  \small{\text{Random sampling function}} & \text{insert text}(r=,) \\
\hline
\end{array}
\end{matrix}
$$



## Other Distributions

</center>

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'odA')">Lognormal</button>
  <button class="tablinks" onclick="openTab(event, 'odB')">Inv Gaussian</button>
  <button class="tablinks" onclick="openTab(event, 'odC')">Single-Parameter Pareto</button>
</div>


<div id="odA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Lognormal</h3>
  <p>

**Lognormal Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & -\infty <\mu <\infty, \sigma>0 \\
\hline
  \small{\text{Probability density}} & \frac{1}{x\sqrt{2\pi}\sigma} \exp\left( -\frac{(\ln x-\mu)^2}{2\sigma^2}\right) \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \Phi\left(\frac{\ln (x)-\mu}{\sigma}\right) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \exp(k\mu+\frac{k^2\sigma^2}{2}) \\
  ~~\mathrm{E}[X^k]  & k>-a \\
\hline
  \small{\text{Limited Expected Value}} & \exp\Big(k\mu+\frac{k^2\sigma^2}{2}\Big)\Phi\Big(\frac{\ln (x)-\mu-k\sigma^2}{\sigma}\Big)+x^k\Big[1-\Phi\Big(\frac{\ln (x)-\mu}{\sigma}\Big)\Big]  \\
  ~~\mathrm{E}[X\wedge x] & \\
\hline
\end{array}
\end{matrix}
$$
```{r eval=TRUE, include=TRUE}
dlognorm=function(x,mu,sigma){
  p=(1/(x*sigma*sqrt(2*pi)))*exp(-((log(x)-mu)/sigma)^2)
  return(p)
}
```

```{r}
mu=20
sigma=12
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dlognorm(X,mu=mu,sigma=sigma),type="l",col="red")
```


</p>
</div>

<div id="odB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Inv Gaussian</h3>
  <p>

**Inverse Gaussian Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & z=\frac{x-\mu}{\mu}~,~y=\frac{x+\mu}{\mu} \\
\hline
  \small{\text{Probability density}} & \Big(\frac{\theta}{2\pi x^3}\Big)^{1/2}\exp\Big(\frac{\theta z^2}{2x}\Big) \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \Phi\Big[z\Big(\frac{\theta}{x}\Big)^{1/2}\Big]+\exp\Big(\frac{2\theta}{\mu}\Big)\Phi\Big[-y\Big(\frac{\theta}{x}\Big)^{1/2}\Big] \\
   ~~F(x) & \\
\hline
  \text{Mean} & \mu \\
  \mathrm{E}[X]  & \\
\hline
  \mathrm{Var[X]} & \frac{\mu^3}{\theta}\\
\hline
  \mathrm{E}[(X\wedge x)^k] & x-\mu x\Phi\Big[z\Big(\frac{\theta}{x}\Big)^{1/2}\Big]-(\mu y)\exp\Big(\frac{2\theta}{\mu}\Big)\Phi\Big[-y\Big(\frac{\theta}{x}\Big)^{1/2}\Big] \\
  &  \\
\hline
\end{array}
\end{matrix}
$$
```{r}
mu=100
theta = 1000
X=seq(from=0,to=100,by=1)
plot(x=X,y=dinvgauss(X,mean=mu,dispersion=theta),type="l",
     ylab="Probability density",col="red",main="Inv Gaussian Distribution")
```


**Inverse Gaussian `R` Commands**


$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dinvgauss}(x=, mean=\mu,dispersion=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pinvgauss}(p=, mean=\mu,dispersion=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qinvgauss}(q=, mean=\mu,dispersion=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rinvgauss}(n=, mean=\mu,dispersion=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="odC" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Single Parameter Pareto</h3>
  <p>

**Single Parameter Pareto Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & \theta~\text{is known.}~,~x>\theta \\
\hline
  \small{\text{Probability density}} & \frac{\alpha\theta^\alpha}{x^{\alpha+1}} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & 1-(\theta/x)^\alpha \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\alpha\theta^k}{\alpha-k} \\
  ~~\mathrm{E}[X^k]  & \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\alpha\theta^k}{\alpha-k}-\frac{k\theta^k}{(\alpha-k)x^{\alpha-k}} \\
  & x \geq\theta \\
\hline
\end{array}
\end{matrix}
$$

```{r}
alpha = 3
theta = 100
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dpareto1(X,shape=alpha,min=theta),type="l",
     ylab="Probability density",col="red",main="Single Parameter Pareto Distribution")
```

**Single Parameter Pareto `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dpareto1}(x=, shape=\alpha,min=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{ppareto1}(p=, shape=\alpha,min=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qpareto1}(q=, shape=\alpha,min=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rpareto1}(n=, shape=\alpha,min=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

## Distributions with Finite Support

</center>

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'fsA')">General Beta</button>
  <button class="tablinks" onclick="openTab(event, 'fsB')">Beta</button>
</div>

<div id="fsA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Generalized Beta</h3>
  <p>

**Generalized Beta Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & 0<x<\theta~,~u=(x/\theta)^\tau \\
\hline
  \small{\text{Probability density}} & \frac{\Gamma(a+b)}{\Gamma(a)\Gamma(b)}u^\alpha(1-u)^{b-1}\frac{\tau}{x} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \beta(a,b;u) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k\Gamma(a+b)\Gamma(a+(k/\tau))}{\Gamma(a)\Gamma(a+b+(k/\tau))} \\
   ~~\mathrm{E}[X^k] & k>-\alpha\tau \\
\hline
  \mathrm{E}[(X\wedge x)^k] & \frac{\theta^k\Gamma(a+b)\Gamma(a+(k/\tau))}{\Gamma(a)\Gamma(a+b+(k/\tau))}\beta(a+(k/\tau),b;u)+x^k[1-\beta(a,b;u)] \\
\hline
\end{array}
\end{matrix}
$$

```{r}
a = 3
b = 5
tau = 2
theta = 1000
X=seq(from = 0, to = 1000, by = 1)
plot(x=X,y=dgenbeta(X,shape1=a,shape2=b,shape3=tau,scale=theta),type="l",
     ylab="Probability density",col="red",main="Generalized Beta Distribution")
```

**Generalized Beta R Commmands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dgenbeta}(x=, shape1=a,shape2=b,shape3=\tau,scale=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pgenbeta}(p=, shape1=a,shape2=b,shape3=\tau,scale=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qgenbeta}(q=, shape1=a,shape2=b,shape3=\tau,scale=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rgenbeta}(n=, shape1=a,shape2=b,shape3=\tau,scale=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

<div id="fsB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Beta</h3>
  <p>

**Beta Functions**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Name} & \text{Function} \\
\hline
  \small{\text{Parameter assumptions}} & u=\frac{x}{\theta},~a>0,~b>0,~0<x<\theta \\
\hline
  \small{\text{Probability density}} & \frac{\Gamma(a+b)}{\Gamma(a)\Gamma(b)} u^a(1-u)^{b-1}\frac{1}{x} \\
 ~~ \small{\text{function }} f(x)& \\
\hline
  \small{\text{Distribution function}} & \beta(a,b;u) \\
   ~~F(x) & \\
\hline
  \textit{k}^{th}~\small{\text{raw moment}} & \frac{\theta^k 
  \Gamma(a+b)\Gamma(a+k)}{\Gamma(a)\Gamma(a+b+1)} \\
  ~~\mathrm{E}[X^k]  & k>-a \\
\hline
  \small{\text{Limited Expected Value}} & \frac{\theta^k a(a+1)\cdots(a+k-1)}{(a+b)(a+b+1)\cdots(a+b+k-1)}\beta(a+k,b;u)+x^k[1-\beta(a,b;u)]  \\
   ~~\mathrm{E}[X\wedge x] & k > -\alpha \\
\hline
\end{array}
\end{matrix}
$$

```{r}
a = 2
b = 4
theta = 1
X=seq(from=0,to=1,by=.0001)
plot(x=X,y=dbeta(X,shape1=a,shape2=b,ncp=theta),type="l",
     ylab="Probability density",col="red",main="Beta Distribution")
```

**Beta `R` Commands**

$$
\begin{matrix}
\begin{array}{l|c}
\hline
  \small{\text{Density function}} & \text{dbeta}(x=, shape1=a,shape2=b,ncp=\theta) \\
\hline
  \small{\text{Distribution function}} & \text{pbeta}(p=, shape1=a,shape2=b,ncp=\theta) \\
\hline
  \small{\text{Quantile function}} & \text{qbeta}(q=, shape1=a,shape2=b,ncp=\theta) \\ 
\hline
  \small{\text{Random sampling function}} & \text{rbeta}(n=, shape1=a,shape2=b,ncp=\theta) \\
\hline
\end{array}
\end{matrix}
$$

</p>
</div>

## Limited Expected Values

</center>

<div class="tab">
  <button class="tablinks" onclick="openTab(event, 'levA')">Functions</button>
  <button class="tablinks" onclick="openTab(event, 'levB')">Graph</button>
</div>


<div id="levA" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Functions</h3>
  <p>

**Limited Expected Value Functions**

$$
{\small
\begin{matrix}
\begin{array}{l|c}
\hline
  \text{Distribuion} & \text{Function} \\
\hline
  \text{GB2} & 
  \frac{\theta\Gamma(\tau+1)\Gamma(\alpha-1)}{\Gamma(\alpha)\Gamma(\tau)}\beta(\tau+1,\alpha-1;\frac{x}{x+\beta})+x[1-\beta(\tau,\alpha;\frac{x}{x+\beta})] \\
\hline
  \text{Burr} & \frac{\theta\Gamma(1+\frac{1}{\tau})\Gamma(\alpha-\frac{1}{\gamma})}{\Gamma(\alpha)}\beta(1+\frac{1}{\gamma},\alpha-\frac{1}{\gamma};1-\frac{1}{1+(x/\theta)^\gamma})+x\Big(\frac{1}{1+(x/\theta)^\gamma}\Big)^\alpha \\
\hline
  \text{Inverse Burr} & \frac{\theta\Gamma(1+(1/\gamma))\Gamma(1-(1/\gamma))}{\Gamma(\gamma)}\beta(\tau+\frac{1}{\gamma},1-\frac{1}{\gamma};\frac{(x/\theta)^\gamma}{1+(x/\theta)^\gamma})+x[1-\Big(\frac{(x/\theta)^\gamma}{1+(x/\theta)^\gamma}\Big)^\tau] \\
\hline
  \text{Pareto} & \\
  \alpha=1 & -\theta \ln \Big(\frac{\theta}{x+\theta}\Big) \\
  \alpha\neq1 & \frac{\theta}{\alpha-1}[1-\Big(\frac{\theta}{x+\theta}\Big)^{\alpha-1}] \\
\hline
  \text{Inverse Pareto} & \theta\tau\int^{x/(x+\theta)}_0~y^\tau(1-y)^{-1}dy+x[1-\Big(\frac{x}{x+\theta}\Big)^\tau] \\
\hline
  \text{Logistic} & \theta\Gamma_1(1+\frac{1}{\gamma})\Gamma(1-\frac{1}{\gamma})\beta(1+\frac{1}{\gamma},1-\frac{1}{\gamma};\frac{(x/\theta)^\gamma}{1+(x/\theta)^\gamma})+x(1-\frac{(x/\theta)^\gamma}{1+(x/\theta)^\gamma})  \\
\hline
  \text{Paralogistic} & \frac{\theta\Gamma(1+\frac{1}{\alpha})\Gamma(\alpha-\frac{1}{\alpha})}{\Gamma(\alpha)}\beta(1+\frac{1}{\alpha},\alpha-\frac{1}{\alpha};1-\frac{1}{1+(x/\theta)^\alpha})+x\Big(\frac{1}{1+(x/\theta)^\alpha}\Big)^\alpha \\
\hline
  \text{Inverse Paralogistic} & \frac{\theta\Gamma(\tau+\frac{1}{\tau})\Gamma(1-\frac{1}{\tau})}{\Gamma(\tau)}\beta(\tau+\frac{1}{\tau},1-\frac{1}{\tau};\frac{(x/\theta)^\tau}{1+(x/\theta)^\tau})+x[1-\Big(\frac{(x/\theta)^\tau}{1+(x/\theta)^\tau}\Big)^\tau] \\
\hline
  \text{Gamma} & \frac{\theta\Gamma(\alpha+1)}{\Gamma(\alpha)}\Gamma(\alpha+k;\frac{x}{\theta})+x[1-\Gamma(\alpha,\frac{x}{\theta})] \\
\hline
  \text{Inverse Gamma} & \frac{\theta\Gamma(\alpha-1)}{\Gamma(\alpha)}[1-\Gamma(\alpha-1;\frac{\theta}{x})]+x\Gamma(\alpha,\frac{\theta}{x}) \\
\hline
  \text{Weibull} & \theta\Gamma(1+\frac{1}{\tau})\Gamma(1+\frac{1}{\tau},\Big(\frac{x}{\theta}\Big)^\tau)+x*\exp(-(x/\theta)^\tau) \\
\hline
  \text{Inverse Weibull} & \theta\Gamma(1-\frac{1}{\tau})[1-\Gamma(1-\frac{1}{\tau};\Big(\frac{\theta}{x}\Big)^\tau)]+x[1-\exp(-(\theta/x)^\tau)] \\
\hline
  \text{Exponential} & \theta(1-\exp(-(x/\theta))) \\
\hline
  \text{Inverse Exponential} & \theta G(0;\frac{\theta}{x})+x(1-\exp(-(\theta/x))) \\
\hline
  \text{Lognormal} & \exp(\mu+\sigma^2/2)\Phi\Big(\frac{\ln (x)-\mu-\sigma^2}{\sigma}\Big)+x[1-\Phi\Big(\frac{\ln (x)-\mu}{\sigma}\Big)] \\
\hline
  \text{Inverse Gaussian} & x-\mu\Big(\frac{x-\mu}{\mu}\Big)\Phi\Big[\Big(\frac{x-\mu}{\mu}\Big)\Big(\frac{\theta}{x}\Big)^{1/2}\Big]-\mu\Big(\frac{x+\mu}{\mu}\Big)\exp\Big(\frac{2\theta}{\mu}\Big)\Phi\Big[-\Big(\frac{x+\mu}{\mu}\Big)\Big(\frac{\theta}{x}\Big)^{1/2}\Big] \\
\hline
  \text{Single-Parameter Pareto} & \frac{\alpha\theta}{\alpha-1}-\frac{\theta^\alpha}{(\alpha-1)x^{\alpha-1}} \\
\hline
  \text{Generalized Beta} & \frac{\theta\Gamma(a+b)\Gamma(a+\frac{1}{\tau})}{\Gamma(a)\Gamma(a+b+\frac{1}{\tau})}\beta(a+\frac{1}{\tau},b;\Big(\frac{x}{\theta}\Big)^\tau)+x\Big[1-\beta(a,b;\Big(\frac{x}{\theta}\Big)^\tau)\Big] \\
\hline
  \text{Beta} & \frac{\theta a}{(a+b)}\beta(a+1,b;\frac{x}{\theta})+x[1-\beta(a,b;\frac{x}{\theta})] \\
\hline
\end{array}
\end{matrix}
}
$$

</p>
</div>


<div id="levB" class="tabcontent">
  <span onclick="this.parentElement.style.display='none'" class="topright">Hide</span>
  <h3>Graphs</h3>
  <p>

**Table of Limited Expected Values**

$$
{\small
\begin{matrix}
\begin{array}{l|c|c}
\hline
  \text{Distribution} & \text{Parameters} & \mathrm{E}[x] & E[X\wedge100] & E[X\wedge250] & E[X\wedge500] &E[X\wedge1000] \\
\hline
  \text{Pareto} & \alpha = 3, \theta = 200 & 100 & 55.55 &80.25 & 91.84 & 97.22  \\ 
\hline
  \text{Exponential} & \theta = 100 & 100 & 63.21 & 91.79 & 99.33 & 99.99 \\
\hline
  \text{Gamma} & \alpha = 2, \theta = 50 & 100 & 72.93 & 97.64 & 99.97 & 100 \\
\hline
  \text{Weibull} & \tau=2, \theta=\frac{200}{\sqrt[]{\pi}} & 100 & 78.99 & 99.82 & 100 & 100 \\
\hline
  \text{GB2} & \alpha = 3,\tau=2,\theta = 100 & 100 & 62.50 & 86.00 & 94.91 & 98.42  \\
\hline
\end{array}
\end{matrix}
}
$$

```{r eval=TRUE, include=FALSE}
require(actuar)
```

```{r eval=TRUE,  echo=FALSE}
X=1:1000
plot(x=X,y=levpareto2(X,3,200),col="red",type="l",xlab="x values", 
     ylab="Limited Expected Value",main="Limted Expected Values for Distributions with the same Expected Value")
lines(x=X,y=levexp(X,rate=1/100),col="blue")
lines(x=X,y=levgamma(X,shape=2,scale=50),col="green")
lines(x=X,y=levweibull(X,shape=2,scale=100/gamma(1.5)),col="orange")
lines(x=X,y=levgenpareto(X,shape1=3,shape2=2,scale=100),col="purple")
legend("bottomright",legend=c("Pareto","Exponential","Gamma","Weibull","GB2"),lty=c(1,1,1,1,1),col=c("red","blue","green","orange","purple"))
```

</p>
</div>


